### 2018-03-14 doc/manuscript.Rmd
minor edits to submission as requested by journal staff

---
bibliography: 
    - /home/luke/Documents/bibliography/bib/bib-db/tagDiabetes.bib
    - /home/luke/Documents/bibliography/bib/bib-db/myrefs.bib
    - /home/luke/Documents/bibliography/bib/bib-db/methods.bib
    - /home/luke/Documents/site/cv/_includes/work.bib
csl: /home/luke/Documents/bibliography/styles/vancouver.csl
output: fost::jlr_manuscript
---

@@

Word count: 200 / 200

@@

## Include captions below using `captioner` package
fig <- captioner::captioner(prefix = 'Figure')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner::captioner(prefix = 'Supplemental Figure')
cite_sf <- pryr::partial(sfig, display = 'cite')

tab <- captioner::captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner::captioner(prefix = 'Supplemental Table')
cite_st <- pryr::partial(stab, display = 'cite')
# usage: cite_st('basicChar')

>>>>

---
bibliography: 
    - /home/luke/Documents/bibliography/bib/bib-db/tagDiabetes.bib
    - /home/luke/Documents/bibliography/bib/bib-db/myrefs.bib
    - /home/luke/Documents/bibliography/bib/bib-db/methods.bib
    - /home/luke/Documents/site/cv/_includes/work.bib
csl: /home/luke/Documents/bibliography/styles/journal-of-lipid-research.csl
output: fost::jlr_manuscript
---

@@

@@

## Include captions below using `captioner` package
fig <- captioner::captioner(prefix = 'Figure')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner::captioner(prefix = 'Supplemental Figure S')
cite_sf <- pryr::partial(sfig, display = 'cite')

tab <- captioner::captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner::captioner(prefix = 'Supplemental Table S')
cite_st <- pryr::partial(stab, display = 'cite')
# usage: cite_st('basicChar')

### 2018-03-14 doc/supplements.Rmd
minor edits to submission as requested by journal staff

# Captions
sfig <- captioner::captioner(prefix = 'Supplemental Figure')
cite_sf <- pryr::partial(sfig, display = 'cite')

tab <- captioner::captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner::captioner(prefix = 'Supplemental Table')
cite_st <- pryr::partial(stab, display = 'cite')

>>>>

# Captions
sfig <- captioner::captioner(prefix = 'Supplemental Figure S')

stab <- captioner::captioner(prefix = 'Supplemental Table S')
